---
title: "Aides Drug"
author: "Lelainy Saavedra"
date: "October 6,2020"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
triUmp <-read.csv(file="triUmpsal.csv",header=TRUE)
triUmpF = filter(triUmp, gender=="F")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->  
In this project we will be trying to see if the new drug triUmpsal is effective by doing a clinical trial. we will be using a cat~cat because we have multiple categories, wheather they are infected or not, gender, drug or no drug and sexual orientation. We will only be considering the females for this trial to see if this drug had any effect.

$H_O$: There is no relationship between the infection rates when a female is taking the placebo or the actual drug.   
$H_A$: There is a relationship between the infection rates when a female is taking the placebo or the actual drug.  




A new  preventative aides drug (triUmpsal) is under test in clinical trials. Consider only the females, does this drug seem effective?  Hint - use dplyr to obtain that subpopulation with the filter command.





# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->


# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results



### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

###Plot barplots
```{r}
barchartGC(~infected + treatment,data=triUmpF)
barchartGC(~infected + treatment,data=triUmpF, type="percent")

```
  
 The bar chart shows that taking the drug vs the placebo may have no effect. 
  
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table1 <- xtabs(~infected + treatment,data=triUmpF)
rowPerc(table1)
colPerc(table1)
```

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
In this Fishers exact test for count data show us that we have a P value = 6.596e-05 < 0.05.  
  It also gives us the odds of a female getting AIDS, when she is taking the drug vs the placebo.  

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

 After looking at the bar chart, the inferential results and the Fishers exact test, we conclude that there is a relationship between a female taking the placebo and taking the drug. Therefore WE REJECT THE NULL HYPOTHESIS.  
 There is a relationship between getting infected and taking the placebo or taking the drug. 




